\thanks{Q. Abarr, J. M. Clem, A. Novikov and D. Seckel are with University of Delaware, Dept. of Physics, Newark, DE 19716.}
\thanks{P. Allison, J. J. Beatty, L. Beaufore, T. Coakley, A. Connolly, P. Dasgupta, J. Flaherty, K. Hughes, P. Linton, W. Luszczak and J. Yao are with Ohio State University, Dept. of Physics, Center for Cosmology and AstroParticle Physics, Columbus, OH 43210. (e-mail: allison.122@osu.edu)}
\thanks{J. Alvarez-Mu\~niz and E. Zas are with Universidade de Santiago de Compostela, Instituto Galego de F\'isica de Altas Enerx\'ias (IGFAE), 15782 Santiago de Compostela, Spain.}
\thanks{T. Anderson, A. Cummings, Y. Ku, C. Welling, S. A. Wissel and A. Zeolla are with Pennsylvania State University, Physics Dept., Inst. for Gravitation and the Cosmos, University Park, PA 16802.}
\thanks{H. Barnett, A. Basharina-Freshville, C. Godden, R. J. Nichol, H. Pumphrey and C. Xie are with University College London, Dept. of Physics and Astronomy, London, United Kingdom.}
\thanks{D. Z. Besson, C. Hornhuber, A. Nozdrina, S. Prohira, M. F. H. Seikh and R. Young are with University of Kansas, Dept. of Physics and Astronomy, Lawrence, KS 66045.}
\thanks{R. Bose, D. Braun, J. Hoffman, L. Lisalda, D. Radomski, B. F. Rauch and G. Simburger are with Washington University in St. Louis, Dept. of Physics, McDonnell Center for the Space Sciences, St. Louis, MO 63130.}
\thanks{B. Chamanbahar, C. Deaconu, A. M. Kofman, S. C. Mackey, Z. Martin, K. McBride, E. Oberla, R. Scrandis, A. G. Vieregg and P. Windischhofer are with University of Chicago, Dept. of Astronomy and Astrophysics, Dept. of Physics, Enrico Fermi Inst., Kavli Inst. for Cosmological Physics, Chicago, IL 60637.}
\thanks{P. Chen, Y. Chen, C.-Y. Kuo, J. Nam, J. Shiao and S.-H. Wang are with National Taiwan University, Dept. of Physics, Grad. Inst. of Astrophys., Leung Center for Cosmology and Particle Astrophysics, Taipei, Taiwan.}
\thanks{L. Cremonesi is with Queen Mary University of London, School. of Physics and Astronomy, London, United Kingdom.}
\thanks{P. W. Gorham, A. Jung and C. Miki are with University of Hawaii-Manoa, Dept. of Physics and Astronomy, Honolulu, HI 96822.}
\thanks{A. Hynous is with NASA Wallops Flight Facility, Wallops Island, VA, 23337}
\thanks{T. C. Liu is with National Pingtung University, Dept. of Applied Physics, Pingtung City, Taiwan.}
