% authorlist for elsarticle publications for PUEO collaboration

\collaboration{PUEO Collaboration}

\address[1]{Dept. of Physics, Univ. of Delaware, Newark, DE 19716.}
\address[2]{Dept. of Physics, Center for Cosmology and AstroParticle Physics, Ohio State Univ., Columbus, OH 43210.}
\address[3]{Instituto Galego de F\'isica de Altas Enerx\'ias (IGFAE), Universidade de Santiago de Compostela, 15782 Santiago de Compostela, Spain}
\address[4]{Pennsylvania State Physics Dept., Inst. for Gravitation and the Cosmos, University Park, PA 16802.}
\address[5]{Dept. of Physics and Astronomy, University College London, London, United Kingdom.}
\address[6]{Dept. of Physics and Astronomy, Univ. of Kansas, Lawrence, KS 66045.}
\address[7]{Dept. of Physics, McDonnell Center for the Space Sciences, Washington Univ. in St. Louis, MO 63130.}
\address[8]{Dept. of Astronomy and Astrophysics, Dept. of Physics, Enrico Fermi Inst., Kavli Inst. for Cosmological Physics, Univ. of Chicago, Chicago, IL 60637.}
\address[9]{Dept. of Physics, Grad. Inst. of Astrophys., Leung Center for Cosmology and Particle Astrophysics, National Taiwan University, Taipei, Taiwan.}
\address[10]{School. of Physics and Astronomy, Queen Mary University of London, London, United Kingdom.}
\address[11]{Dept. of Physics and Astronomy, Univ. of Hawaii, Manoa, HI 96822.}
\address[12]{NASA Wallops Flight Facility, Wallops Island, VA, 23337}
\address[13]{Dept. of Applied Physics, National Pingtung University, Pingtung City, Taiwan}
\address[14]{National Nano Device Laboratories, Hsinchu 300, Taiwan.}
\address[15]{Pennsylvania State Astronomy and Astrophysics Dept., University Park, PA 16802.}


\author[1]{Q.~Abarr}
\author[2]{P.~Allison}
\author[3]{J.~Alvarez-Mu\~niz}
\author[4]{T.~Anderson}
\author[5]{H.~Barnett}
\author[5]{A.~Basharina-Freshville}
\author[2]{J.~J.~Beatty}
\author[2]{L.~Beaufore}
\author[6]{D.~Z.~Besson}
\author[7]{R.~Bose}
\author[7]{D.~Braun}
\author[8]{B.~Chamanbahar}
\author[9]{P.~Chen}
\author[9]{Y.~Chen}
\author[1]{J.~M.~Clem}
\author[2]{T.~Coakley}
\author[2]{A.~Connolly}
\author[10]{L.~Cremonesi}
\author[4]{A.~Cummings}
\author[2]{P.~Dasgupta}
\author[8]{C.~Deaconu}
\author[2]{J.~Flaherty}
\author[5]{C.~Godden}
\author[11]{P.~W.~Gorham}
\author[6]{C.~Hornhuber}
\author[7]{J.~Hoffman}
\author[2]{K.~Hughes}
\author[12]{A.~Hynous}
\author[11]{A.~Jung}
\author[8]{A.~M.~Kofman}
\author[4]{Y.~Ku}
\author[9]{C.-Y.~Kuo}
\author[2]{P.~Linton}
\author[7]{L.~Lisalda}
\author[13]{T.~C.~Liu}
\author[2]{W.~Luszczak}
\author[8]{S.~C.~Mackey}
\author[8]{Z.~Martin}
\author[8]{K.~McBride}
\author[11]{C.~Miki}
\author[9]{J.~Nam}
\author[5]{R.~J.~Nichol}
\author[1]{A.~Novikov}
\author[6]{A.~Nozdrina}
\author[8]{E.~Oberla}
\author[6]{S.~Prohira}
\author[5]{H.~Pumphrey}
\author[7]{D.~Radomski}
\author[7]{B.~F.~Rauch}
\author[8]{R.~Scrandis}
\author[1]{D.~Seckel}
\author[6]{M.~F.~H.~Seikh}
\author[9,14]{J.~Shiao}
\author[7]{G.~Simburger}
\author[8]{A.~G.~Vieregg}
\author[9]{S.-H.~Wang}
\author[4]{C.~Welling}
\author[8]{P.~Windischhofer}
\author[4,15]{S.~A.~Wissel}
\author[5]{C.~Xie}
\author[2]{J.~Yao}
\author[6]{R.~Young}
\author[3]{E.~Zas}
\author[4]{A.~Zeolla}
