% Collaboration institute file for PUEO in aas format
%% \input this file in the preamble (make sure you also do the author file in the body!) 

\newcommand{\atUD}{\affiliation{Dept. of Physics, Univ. of Delaware, Newark, DE 19716.}}
\newcommand{\atOSU}{\affiliation{Dept. of Physics, Center for Cosmology and AstroParticle Physics, Ohio State Univ., Columbus, OH 43210.}}
\newcommand{\atSantiago}{\affiliation{Instituto Galego de F\'isica de Altas Enerx\'ias (IGFAE), Universidade de Santiago de Compostela, 15782 Santiago de Compostela, Spain}}
\newcommand{\atPSU}{\affiliation{Pennsylvania State Physics Dept., Inst. for Gravitation and the Cosmos, University Park, PA 16802.}}
\newcommand{\atUCL}{\affiliation{Dept. of Physics and Astronomy, University College London, London, United Kingdom.}}
\newcommand{\atKU}{\affiliation{Dept. of Physics and Astronomy, Univ. of Kansas, Lawrence, KS 66045.}}
\newcommand{\atWU}{\affiliation{Dept. of Physics, McDonnell Center for the Space Sciences, Washington Univ. in St. Louis, MO 63130.}}
\newcommand{\atUC}{\affiliation{Dept. of Astronomy and Astrophysics, Dept. of Physics, Enrico Fermi Inst., Kavli Inst. for Cosmological Physics, Univ. of Chicago, Chicago, IL 60637.}}
\newcommand{\atNTU}{\affiliation{Dept. of Physics, Grad. Inst. of Astrophys., Leung Center for Cosmology and Particle Astrophysics, National Taiwan University, Taipei, Taiwan.}}
\newcommand{\atQMUL}{\affiliation{School. of Physics and Astronomy, Queen Mary University of London, London, United Kingdom.}}
\newcommand{\atUH}{\affiliation{Dept. of Physics and Astronomy, Univ. of Hawaii, Manoa, HI 96822.}}
\newcommand{\atWallops}{\affiliation{NASA Wallops Flight Facility, Wallops Island, VA, 23337}}
\newcommand{\atNPTU}{\affiliation{Dept. of Applied Physics, National Pingtung University, Pingtung City, Taiwan}}
\newcommand{\atNNDL}{\affiliation{National Nano Device Laboratories, Hsinchu 300, Taiwan.}}
\newcommand{\atPSU2}{\affiliation{Pennsylvania State Astronomy and Astrophysics Dept., University Park, PA 16802.}}
