% authorlist for elsarticle publications for PUEO collaboration

\author[a]{Q.~Abarr}
\author[b]{P.~Allison}
\author[c]{J.~Alvarez-Mu\~niz}
\author[d]{T.~Anderson}
\author[e]{H.~Barnett}
\author[e]{A.~Basharina-Freshville}
\author[b]{J.~J.~Beatty}
\author[b]{L.~Beaufore}
\author[f]{D.~Z.~Besson}
\author[g]{R.~Bose}
\author[g]{D.~Braun}
\author[h]{B.~Chamanbahar}
\author[i]{P.~Chen}
\author[i]{Y.~Chen}
\author[a]{J.~M.~Clem}
\author[b]{T.~Coakley}
\author[b]{A.~Connolly}
\author[j]{L.~Cremonesi}
\author[d]{A.~Cummings}
\author[b]{P.~Dasgupta}
\author[h]{C.~Deaconu}
\author[b]{J.~Flaherty}
\author[e]{C.~Godden}
\author[k]{P.~W.~Gorham}
\author[f]{C.~Hornhuber}
\author[g]{J.~Hoffman}
\author[b]{K.~Hughes}
\author[l]{A.~Hynous}
\author[k]{A.~Jung}
\author[h]{A.~M.~Kofman}
\author[d]{Y.~Ku}
\author[i]{C.-Y.~Kuo}
\author[b]{P.~Linton}
\author[g]{L.~Lisalda}
\author[m]{T.~C.~Liu}
\author[b]{W.~Luszczak}
\author[h]{S.~C.~Mackey}
\author[h]{Z.~Martin}
\author[h]{K.~McBride}
\author[k]{C.~Miki}
\author[i]{J.~Nam}
\author[e]{R.~J.~Nichol}
\author[a]{A.~Novikov}
\author[f]{A.~Nozdrina}
\author[h]{E.~Oberla}
\author[f]{S.~Prohira}
\author[e]{H.~Pumphrey}
\author[g]{D.~Radomski}
\author[g]{B.~F.~Rauch}
\author[h]{R.~Scrandis}
\author[a]{D.~Seckel}
\author[f]{M.~F.~H.~Seikh}
\author[i,n]{J.~Shiao}
\author[g]{G.~Simburger}
\author[h]{A.~G.~Vieregg}
\author[i]{S.-H.~Wang}
\author[d]{C.~Welling}
\author[h]{P.~Windischhofer}
\author[d,o]{S.~A.~Wissel}
\author[e]{C.~Xie}
\author[b]{J.~Yao}
\author[f]{R.~Young}
\author[c]{E.~Zas}
\author[d]{A.~Zeolla}


\affiliation[a]{Dept. of Physics, Univ. of Delaware, Newark, DE 19716.}
\affiliation[b]{Dept. of Physics, Center for Cosmology and AstroParticle Physics, Ohio State Univ., Columbus, OH 43210.}
\affiliation[c]{Instituto Galego de F\'isica de Altas Enerx\'ias (IGFAE), Universidade de Santiago de Compostela, 15782 Santiago de Compostela, Spain}
\affiliation[d]{Pennsylvania State Physics Dept., Inst. for Gravitation and the Cosmos, University Park, PA 16802.}
\affiliation[e]{Dept. of Physics and Astronomy, University College London, London, United Kingdom.}
\affiliation[f]{Dept. of Physics and Astronomy, Univ. of Kansas, Lawrence, KS 66045.}
\affiliation[g]{Dept. of Physics, McDonnell Center for the Space Sciences, Washington Univ. in St. Louis, MO 63130.}
\affiliation[h]{Dept. of Astronomy and Astrophysics, Dept. of Physics, Enrico Fermi Inst., Kavli Inst. for Cosmological Physics, Univ. of Chicago, Chicago, IL 60637.}
\affiliation[i]{Dept. of Physics, Grad. Inst. of Astrophys., Leung Center for Cosmology and Particle Astrophysics, National Taiwan University, Taipei, Taiwan.}
\affiliation[j]{School. of Physics and Astronomy, Queen Mary University of London, London, United Kingdom.}
\affiliation[k]{Dept. of Physics and Astronomy, Univ. of Hawaii, Manoa, HI 96822.}
\affiliation[l]{NASA Wallops Flight Facility, Wallops Island, VA, 23337}
\affiliation[m]{Dept. of Applied Physics, National Pingtung University, Pingtung City, Taiwan}
\affiliation[n]{National Nano Device Laboratories, Hsinchu 300, Taiwan.}
\affiliation[o]{Pennsylvania State Astronomy and Astrophysics Dept., University Park, PA 16802.}


\collaboration{PUEO Collaboration}

